Analysis

### 2020-01-16 script/analysis.Rmd

@@

sink("output/tables/desc.html")
kableExtra::kable(tab03,format = "html",booktabs=T ,row.names = F,col.names = c("Dimensión","N","Variable/niveles","Media(DS)","Min","Max")) %>%
  kable_styling() %>%
    collapse_rows(columns = 1,valign = "middle")
sink()
```

>>>>

```{r}
options(knitr.kable.NA = '')

@@

sink("output/tables/desc.html")
kableExtra::kable(tab03,format = "html",booktabs=T ,row.names = F,col.names = c("Dimensión","N","Variable/niveles","Media(DS)","Min","Max")) %>%
  kable_styling() %>%
    collapse_rows(columns = 1,valign = "middle")
sink()
